A multi-dimensional percolation approach to characterize sustainable mega-city regions

### 2018-10-17 Docs/Marami2018/Communication/marami2018.tex
consolidated_data
data_sources
more_figs

\sframe{Networks and territories}{

@@

@@

	%\includegraphics[width=0.52\textwidth]{figures/}

	\footnotesize
%\textit{Source: Wikipedia}

@@

@@

@@

>>>>

\sframe{Morphologies of networks and territories}{

@@

% -> visu OSM : see Metropolitan region ; plus positioning of Avignon ; Q of sustainibility ?

@@

	\includegraphics[width=1.2\textwidth]{figures/roadssouth.png}

	\footnotesize
\textit{Source: OpenStreetMap}

@@

% here extracts from Claire's work
% Lagesse, C., Bordin, P., & Douady, S. (2015). A spatial multi-scale object to analyze road networks. Network Science, 3(1), 156-181. -> nice picture Avignon

\textit{Multiple dimensions to characterize road networks}

{
\centering
\includegraphics[width=\textwidth,height=0.7\textheight]{figures/avignon_claire.png}
}

Lagesse, C., Bordin, P., \& Douady, S. (2015). A spatial multi-scale object to analyze road networks. Network Science, 3(1), 156-181. \cite{lagesse2015spatial}

@@

% similar to 
%Cottineau, C., Finance, O., Hatna, E., Arcaute, E., & Batty, M. (2018). Defining urban clusters to detect agglomeration economies. Environment and Planning B: Urban Analytics and City Science, 2399808318755146.

\textbf{Network percolation: } \textit{progressive occupation/connection of nodes of a network} \cite{callaway2000network}

Application to the study of cities:

\begin{itemize}
	\item modeling urban growth \cite{makse1998modeling}
	\item endeogenous determination of regions \cite{arcaute2016cities}
	\item characterization of spatial point patterns \cite{huynh2018characterisation}
\end{itemize}

\textit{Towards complementary dimensions to condition road network percolation}

$\rightarrow$ similar to \cite{cottineau2018defining} to define urban areas

@@

\sframe{Extrapolating transportation flows}{

% detail method to extrapolate parameters of gravity flows

% interesting result : compare these emission with the synthetic ? (then just a refinment ?) -> yes, better. show new Pareto fronts with this fixed parameters for only emissions, and varying for economic ?
